Insert title of project here

### 2022-04-11 Draft Report/Draft Project.Rmd
lets see

---
output: 
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    number_sections: yes
geometry: margin=2.54cm
title: "Insert title of project here"
subtitle: "Web address for GitHub repository"
author: "Name"
fontsize: 12pt
mainfont: Times New Roman
---
```{r, initialize}
# Set your working directory
getwd()
knitr::opts_knit$set(root.dir = '/xxxDesktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject')

@@

### Gather Data Sources
```{r load datasources}
# Load your datasets
NRICali <- read.csv('~/Desktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject/Data Sources/NRI_Table_CensusTracts_California/NRI_Table_CensusTracts_California.csv', stringsAsFactors = TRUE)
NRINorCar <- read.csv('~/Desktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject/Data Sources/NRI_Table_CensusTracts_NorthCarolina/NRI_Table_CensusTracts_NorthCarolina.csv', stringsAsFactors = TRUE)
NRIFlor <- read.csv('~/Desktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject/Data Sources/NRI_Table_CensusTracts_Florida/NRI_Table_CensusTracts_Florida.csv', stringsAsFactors = TRUE)
EJScreen21 <- read.csv('~/Desktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject/Data Sources/EJSCREEN_2021_StatePctile_Tracts.csv',stringsAsFactors = TRUE)
```

@@

```{r EJScreen Filters}
EJ_filter <- EJScreen21 %>%
  select(ID,STATE_NAME,contains("INCPCT"),contains("HSPCT"),LINGISOPCT,PRE1960PCT,contains("LDPNT"),contains("PM25"))
```

### Present Descriptive Statistics and Maps

>>>>

---
output: 
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    number_sections: yes
geometry: margin=2.54cm
title: "Insert title of project here"
subtitle: "Web address for GitHub repository"
author: "Name"
fontsize: 12pt
mainfont: Times New Roman
---
```{r, initialize}
# Set your working directory
getwd()
knitr::opts_knit$set(root.dir = '/Desktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject')

@@

### Gather Data Sources
```{r load datasources}
# Load your datasets
NRICali <- read.csv('~/Desktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject/Potential Data Sources/NRI_Table_CensusTracts_California/NRI_Table_CensusTracts_California.csv', stringsAsFactors = TRUE)
NRINorCar <- read.csv('~/Desktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject/Potential Data Sources/NRI_Table_CensusTracts_NorthCarolina/NRI_Table_CensusTracts_NorthCarolina.csv', stringsAsFactors = TRUE)
NRIFlor <- read.csv('~/Desktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject/Potential Data Sources/NRI_Table_CensusTracts_Florida/NRI_Table_CensusTracts_Florida.csv', stringsAsFactors = TRUE)
EJScreen21 <- read.csv('~/Desktop/Duke MPP/Environ Data /872 Final Project/AmanfuJaniRoberton_ENV872_EDA_FinalProject/Potential Data Sources/EJSCREEN_2021_StatePctile_Tracts.csv',stringsAsFactors = TRUE)
```

@@

```{r EJScreen Filters}
EJ_filter <- EJScreen21 %>%
  select(ID,STATE_NAME,contains("INCPCT"),contains("HSPCT"),LINGISOPCT,PRE1960PCT,contains("LDPNT"),contains("PM25"))

```

### Present Descriptive Statistics and Maps
Add in Shape Files 
https://www.census.gov/geographies/mapping-files/time-series/geo/cartographic-boundary.html
```{r census tracts}
california_tract <- st_read('./Potenital Data Sources/cb_2020_cali_tract_500k/cb_2020_06_tract_500k.shp')
norcar_tract <- st_read('./Potential Data Sources/cb_2020_norcar_tract_500k/cb_2020_37_tract_500k.shp')
florida_tract <- st_read('./Potential Data Sources/cb_2020_flor_tract_500k/cb_2020_12_tract_500k.shp')
```
